---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# RegAssure

<!-- badges: start -->
[![R-CMD-check](https://github.com/nrubiog/RegAssure/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/nrubiog/RegAssure/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The RegAssure package is designed to simplify and enhance the process of validating regression model assumptions in R. It provides a comprehensive set of tools for evaluating key assumptions such as linearity, homoscedasticity, independence, normality, and collinearity, contributing to the reliability of analytical results.

## Installation

You can easily install RegAssure from GitHub using the devtools package:

``` r
# install.packages("devtools")
devtools::install_github("nrubiog/RegAssure")
```

## Example: Linear Regression

Here's a basic example showcasing how RegAssure can be used to enhance linear regression analysis:

```{r example}
# Install the package
# devtools::install_github("nrubiog/RegAssure")

# Load the package
library(RegAssure)

# Create a regression model
lm_model <- lm(mpg ~ wt + hp, data = mtcars)

# Check assumptions
check_lm_assumptions(lm_model)
```

## Example: Logistic Regression

Here's an additional example demonstrating the use of RegAssure with logistic regression:

```{r}
# Load the package

library(RegAssure)
library(titanic)

# Load the dataframe
titanic <- titanic_train

# Create a binary logistic regression model
logit_model <- glm(Survived ~ Pclass + Sex, data = titanic, family = "binomial")

# Check assumptions for binary logistic regression
check_logit(logit_model, data = titanic, tipo_modelo = "binario", vars_numericas = "Pclass", y = "Survived")
```

## Example: storing data

Here's an example of how to use the get_predict() function to compare real and predicted values from a model:

```{r}
# Load the package
library(RegAssure)

# Create a regression model
lm_model <- lm(mpg ~ wt + hp, data = mtcars)

# Get predictions and compare with real values
predictions <- get_predict(lm_model, mtcars, mtcars$mpg, n = 3)

# Print the results
print(predictions[1:7,])
```


By incorporating RegAssure into your workflow, you can streamline the process of assessing and addressing regression model assumptions, leading to more informed decision-making.
